---
title: "Presentation Ninja"
subtitle: "<br/>with xaringan"
author: "Yihui Xie"
date: "2016/12/12"
output:
  xaringan::moon_reader:
    lib_dir: libs
    yolo: FALSE
    seal: FALSE
    css: ["default", "extra.css"]
    self_contained: FALSE
    nature:
      highlightStyle: github
      highlightLines: TRUE
      countIncrementalSlides: FALSE
      ratio: '16:9'
---
class: center, middle, title-slide

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

<style>
.remark-slide-number {
  color: #ffff;
  margin: 0px 0px 0px 0px;
  padding: 20px;
  font-family: Tahoma, Geneva, sans-serif;
}


h1, h2, h3 {
  font-family: "Yanone Kaffeesatz", Tahoma, Geneva, sans-serif;
  font-weight: normal;
}


.footer {
  position: absolute;
  right: 0;
  bottom: 0;
  left: 0;
  padding: 1rem;
  background-color: #efefef;
  text-align: center;
}

exercise {
  color: #006d9e;
  font-weight:  bold;
}


</style>

<img src = 'img/cas.png'>

<h1 class="title"> 2017 CAS Spring Meeting </h1>
<h2 class="title"> <span class="red"> Introduction </span> to <code class="remark-inline-code">R</code>: Reading Data</h2>

<h3 class="title"> Rajesh Sahasrabuddhe</h3>

<h3 class="title"> Alexandra Taggart</h3>
<br>
<img src = 'img/logo.png' height="25px">

---
layout: true


<footer>
<img src = 'img/logo.png' height="15px" style = "position: absolute; right: 0px; bottom: 30px; left: 30px; text-align: center;">
</footer>

---

# Setup

--

<ol>
  <li> Install R <a href="https://www.r-project.org/">https://www.r-project.org/</a> </li>
--

  <li> Install R Studio <a href="https://www.rstudio.com/products/rstudio/download2/">https://www.rstudio.com/products/rstudio/download2/</a></li>

--

  <li> Install Packages </li>
  
  <ol>
    <li> from R Studio GUI </li>
--
    <li> from console <br><code class="remark-inline-code">install.packages(pkgs = 'tidyverse')</code></li>
    <li> <code class="remark-inline-code">devtools::install_github()</code></li>
  </ol>
</ol>

---

# Basics

<ol>
  <li>Assignment operator (<code class="remark-inline-code"><-</code>)</li>
  <li>Help (<code class="remark-inline-code">?, ??</code>)</li>
  <li>Classes (<code class="remark-inline-code">"numeric", "logical", "character" or "list", "matrix", "array", "factor" and "data.frame"</code>)</li>
  <li>The structure function (<code class="remark-inline-code">str</code>)</li>
  <li>The <code class="remark-inline-code">tidyverse</code>
  <li>Styleguide <a href="http://adv-r.had.co.nz/Style.html">http://adv-r.had.co.nz/Style.html</a></li>
</ol>

---

# Read Data

<ol>
  <li> Comma-separated values (<code class="remark-inline-code">read.csv, readr::read_csv</code>)</li>
  <li> Comma-separated values (<code class="remark-inline-code">readxl::read_excel</code>)</li>
</ol>

---

# Exercise 1

Locate the <code class="remark-inline-code">mtcars.csv</code> file that comes with <code class="remark-inline-code">readr</code>
```{r}
library(readr)
readr_example("mtcars.csv")
```
<exercise>Read this file using <code class="remark-inline-code">read.csv</code> and assign this to object <code class="remark-inline-code">cas01</code><br>
<exercise>Read this file using <code class="remark-inline-code">read_csv</code> and assign this to object <code class="remark-inline-code">cas02</code><br>
What is the difference between the files?
</exercise>

---

# Solution 1

```{r, message=FALSE}
fn <- readr_example("mtcars.csv")
cas01 <- read.csv(file = fn)
cas02 <- read_csv(file = fn)
class(cas01)
class(cas02)
```

---

# Exercise 2

Locate the <code class="remark-inline-code">mtcars.csv</code> file that comes with <code class="remark-inline-code">readr</code>
```{r}
library(readxl)
readxl_example('deaths.xlsx')
```
<exercise>Read this file using <code class="remark-inline-code">read_excel</code> and assign this to object <code class="remark-inline-code">cas03</code><br>
How many row and columns does this dataframe contain?
</exercise>

---

# Solution 2: Try #1

```{r, message=FALSE}
fn <- readxl_example('deaths.xlsx')
cas03 <- read.csv(fn)
str(cas03)
```

---

# Solution 2: Try #2

```{r}
fn <- readxl_example('deaths.xlsx')
cas03 <- read_excel(fn, sheet = 'arts' , range = 'a5:f15')
str(cas03)
```


---

# Read in CAS Data
```{r}
auto_dat_cas <- read_csv('http://www.casact.org/research/reserve_data/ppauto_pos.csv')
```




