---
title: "Presentation Ninja"
subtitle: "<br/>with xaringan"
author: "Yihui Xie"
date: "2016/12/12"
output:
  xaringan::moon_reader:
    lib_dir: libs
    yolo: FALSE
    seal: FALSE
    css: ["default", "extra.css"]
    self_contained: FALSE
    nature:
      highlightStyle: github
      highlightLines: TRUE
      countIncrementalSlides: FALSE
      ratio: '16:9'
---
class: center, middle, title-slide

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

<style>
.remark-slide-number {
  color: #ffff;
  margin: 0px 0px 0px 0px;
  padding: 20px;
  font-family: "Droid Serif","Palatino Linotype","Book Antiqua",Palatino,"Microsoft YaHei","Songti SC",serif;
}

h1, h2, h3 {
  font-family: "Yanone Kaffeesatz", Tahoma, Geneva, sans-serif;
  font-weight: normal;
}


.footer {
  position: absolute;
  right: 0;
  bottom: 0;
  left: 0;
  padding: 1rem;
  background-color: #efefef;
  text-align: center;
}


</style>



<img src = 'img/cas.png'>

<h1 class="title"> 2017 CAS Spring Meeting </h1>
<h2 class="title"> <span class="red"> Introduction </span> to <code class="remark-inline-code">R</code>: Fitting Models and Saving Results</h2>

<h3 class="title"> Rajesh Sahasrabuddhe</h3>

<h3 class="title"> Alexandra Taggart</h3>

<img src = 'img/logo.png' height="25px">

---
layout: true


<footer>
<img src = 'img/logo.png' height="15px" style = "position: absolute; right: 0px; bottom: 30px; left: 30px; text-align: center;">
</footer>

---

# Basics

<ol>
  <li>A mathematical model is a description of a system using mathematical concepts and language.</li>
  <li>Models are R objects like any others</li>
  <li>Common Actuarial Models (not a complete list)</li>
  <ol>
    <li>Linear Models (Relationships)</li>
    <li>Distributions</li>
  </ol>
</ol>


---

# The Linear Model (OLS)

```{r}
lm1 <- lm(mpg ~ wt, data = mtcars)
```

<ol>
  <li> Summary (via) <code>summary.lm</code></li>
  <li> Predict (via) <code>summary.lm</code></li>
  <li><code>lm.influence</code> and <code>confint</code></li>
<ol>

---

# The Linear Model (OLS)

```{r}
summary(lm1)
```


---

# The Linear Model (OLS)

```{r, fig.height=5}
plot(lm1, which = 1:2)
```
---

# The Linear Model (OLS)

```{r, fig.height=5}
plot(lm1, which = c(3,5))
```
---

# The Linear Model (OLS)

```{r, fig.height=5}
confint(lm1)
predict(object = lm1, newdata = data.frame(wt = 3))
```

---

# The Linear Model (OLS)

```{r, fig.height=5}
new_mpg <- predict(object = lm1, newdata = data.frame(wt = 3))
plot(x = mtcars$wt, y = mtcars$mpg)
points(x = 3, y = new_mpg, col = "blue", pch = 19)
abline(v = 3, lty = 'dotted', col = 'blue')
abline(h = new_mpg, lty = 'dotted', col = 'blue')
```

---
# Exercise 1


Fit a linear model regressing distance on speed in the <code>datasets::cars</code> data.
<ol>
<li>Provide the coefficient of distance</li>
<li>Plot the model (in orange) against the data (in blue).</li>
<li>Extract the residual of the 10th data point</li>
</ol>

---
# Solution 1

```{r, fig.height=4}
plot(cars$speed, cars$dist, col = 'blue')
lm2 <- lm(dist ~ speed, data = cars)
abline(lm2, col= "orange")
```
---
# Solution 1

```{r, fig.height=3}
coefficients(lm2)
confint(lm2)
#str(lm2)
lm2$residuals[10]
```

---
# Solution 1

```{r, fig.height=4}
plot(cars$speed, cars$dist, col = 'blue')
abline(lm2, col = 'orange')
points(cars$speed[10], cars$dist[10], col = 'red', pch = 19)
new_y <- predict(lm2, newdata = data.frame(speed = cars$speed[10]))
points(cars$speed[10], new_y, col = 'red', pch = 19)
text(x = cars$speed[10] + .5, y = mean(new_y, cars$dist[10]) - 2, col = ' red',
  labels = paste('Resid =', round(cars$dist[10] - new_y, 3)), adj = c(0,0.5))

```
---

# Exercise 2

The <code>mixtools</code> packages includes functions to fit finite mixture distributions.
<ol>
  <li> Review the faithful dataset via <code>?faithful</code></li>
  <li> Use the normalmixEM function to fit a two component mixture of normals to the <code>waiting</code> variable in the <code>faithful</code> data using the following assumptions:</li>
  <ol>
    <li> Using a starting seed of <code>12345</code></li>
    <li> Using a 50/50 weighting for the starting mix rates </li>
    <li> With the components centered 55 and 80</li>
    <li> With each of the components have a standard deviations of 5</li>
  </ol>
  <li> Report the parameters of the model </li>
  <li> Create a plot that compares the data and models</li>

---

# Solution 2



```{r}
# install.packages(mixtools)
library(mixtools)
set.seed(12345)
wait1 <- normalmixEM(faithful$waiting, lambda = .5, mu = c(55, 80), sigma = 5)
summary(wait1)

```
---

# Solution 2

```{r, fig.height=5}
# install.packages(mixtools)
plot(wait1, density = TRUE, cex.axis = 1.4, cex.lab = 1.4, cex.main = 1.8, 
  main2 = "Time between Old Faithful eruptions", xlab2 = "Minutes", which = 2)
```
