---
title: "Presentation Ninja"
subtitle: "<br/>with xaringan"
author: "Yihui Xie"
date: "2016/12/12"
output:
  xaringan::moon_reader:
    lib_dir: libs
    yolo: FALSE
    seal: FALSE
    css: ["default", "extra.css"]
    self_contained: FALSE
    nature:
      highlightStyle: github
      highlightLines: TRUE
      countIncrementalSlides: FALSE
      ratio: '16:9'
---
class: center, middle, title-slide

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

<style>
.remark-slide-number {
  color: #ffff;
  margin: 0px 0px 0px 0px;
  padding: 20px;
  font-family: "Droid Serif","Palatino Linotype","Book Antiqua",Palatino,"Microsoft YaHei","Songti SC",serif;
}

h1, h2, h3 {
  font-family: "Yanone Kaffeesatz", Tahoma, Geneva, sans-serif;
  font-weight: normal;
}


.footer {
  position: absolute;
  right: 0;
  bottom: 0;
  left: 0;
  padding: 1rem;
  background-color: #efefef;
  text-align: center;
}


</style>



<img src = 'img/cas.png'>

<h1 class="title"> 2017 CAS Spring Meeting </h1>
<h2 class="title"> <span class="red"> Introduction </span> to <code class="remark-inline-code">R</code>: Data Visualization</h2>

<h3 class="title"> Rajesh Sahasrabuddhe</h3>

<h3 class="title"> Alexandra Taggart</h3>

<img src = 'img/logo.png' height="25px">

---
layout: true


<footer>
<img src = 'img/logo.png' height="15px" style = "position: absolute; right: 0px; bottom: 30px; left: 30px; text-align: center;">
</footer>

---

# Basics: The Pipe

<ol>
  <li>The pipe, <code>%>%</code>, comes from the <code>magrittr</code> package by Stefan Milton Bache. Packages in the tidyverse load <code>%>%</code> for you automatically, so you don’t usually load magrittr explicitly.</li>

  <li>Ctrl + Shift + M is the keyboard shortcut for the pipe.</li>

  <li>The pipe allows for much more readable code</li>

  <li> x %>% foo(y) %>% bar() is the same as bar(foo(x, y)) </li>
</ol>


---


# Popular Plotting Systems

<ol>
  <li>Raster Graphics</li>
  <ol>
    <li> ggplot (<code class="remark-inline-code">ggplot2</code>) </li>
    <li> base </li>
    <li> lattice </li>
  </ol>
  <li>HTML Canvas</li>
  <ol>
    <li>rbokeh</li>
    <li>googlevis</li>
    <li>highcharts (not free for commercial use)</li>
  </ol>
  <li>Primary Differences</li>
  <ol>
    <li>Form of output</li>
    <li>Code Structure</li>
  </ol>
</ol>  
---

# Scatter Plot via Base Graphics

```{r, fig.height=5, message=FALSE, warning=FALSE}
plot(x = iris$Sepal.Length, y = iris$Sepal.Width)

```

---

# Scatter Plot via Rbokeh

```{r, fig.height=5, message=FALSE, warning=FALSE}
library(rbokeh)
figure() %>% ly_points(Sepal.Length, Sepal.Width, data = iris)
```

---

# Scatter Plot via Ggplot

```{r, fig.height=5, message=FALSE, warning=FALSE}
library(ggplot2)
ggplot(data = iris, mapping = aes(x = Sepal.Length, y = Sepal.Width)) + geom_point()

```

---

# Scatter Plot via highcharter


```{r, fig.height=3, message=FALSE, warning=FALSE}
library(highcharter)
highchart() %>% 
  hc_add_series_scatter(x = iris$Sepal.Length, y = iris$Sepal.Width)
```

---

# Exercise 1

```{r}
head(mtcars)
```

Create a scatterplot of mpg v weight using base and one other plotting system (suggest ggplot)

---

# Solution 1.1

```{r, fig.height=5, message=FALSE, warning=FALSE}
plot(x = mtcars$wt, y = mtcars$mpg)
```
---

# Solution 1.2

```{r, fig.height=5, message=FALSE, warning=FALSE}
ggplot(data = mtcars, mapping = aes(x = wt, y = mpg)) + geom_point()
```

---

# Exercise 2

```{r, fig.height=5, message=FALSE, warning=FALSE}
head(faithful)
```

Create a histogram of the eruptions variable using base plotting and one other plotting system

---

# Solution 2.1

```{r, fig.height=5, message=FALSE, warning=FALSE}
hist(x = faithful$eruptions)
```
---

# Solution 2.2

```{r, fig.height=5, message=FALSE, warning=FALSE}
figure(width = 600, height = 400) %>%
  ly_hist(eruptions, data = faithful)
```
